Soss

### 2019-12-22 paper/paper.tex
Start on related work

@@

\bibliographystyle{acm-reference-format}
\bibliography{probprog-2020-instructions}

>>>>

\section{Related Work}

The idea of code generation and symbolic simplification in an embedded PPL goes back to \emph{Passage} \cite{Scherrer2012}.

\emph{Hakaru} \cite{narayanan2016probabilistic} takes a more ambitious symbolic approach in a stand-alone PPL, allowing a wider variety of program transformations.

Soss began with a goal of representing models with continuous, fixed-dimensionality parameter spaces, inspried by \emph{Stan} \cite{stan:2017}.

\emph{Gen} \cite{Cusumano-Towner:2019}

\emph{Turing} \cite{ge2018t}

@@

\bibliographystyle{acm-reference-format}
\bibliography{ref}
